
# Analysis
```{r load-field-data, cache=TRUE}
var_ls <- c("obs_id",        "yild_vl",         "s_rate",          "n_rate",
            "elevatn",       "f290404",         "f485941",         "slope",                          "aspect",        "curv",            "twi" ,            "tpi",                            "ecd",           "ecs",             "x",               "geometry")
```

```{r load-data, cache=FALSE}
data_sf <- read_data(ffy, var_ls)

w_field_data$crop_price <- historical_price[year == strsplit(ffy, "_")[[1]][3], corn]
w_field_data$n_price <- historical_price[year == strsplit(ffy, "_")[[1]][3], n]
w_field_data$s_price <- historical_price[year == strsplit(ffy, "_")[[1]][3], s]

analysis_res_g <- w_field_data %>% 
  mutate(data = list(data_sf)) %>% 
  rowwise() %>%
  mutate(
    field_vars = list(
      find_field_vars(data)
    )
  ) 
 
```

## SCAM/GAM Yield Response Function Estimation and Optimal Rates
### GAM Estimation
```{r gam, cache=FALSE}
analysis_res_gam <- analysis_res_g %>% 
  mutate(gam_res = list(
    run_scam_gam_ec(data = data, field_vars = field_vars)
  )) %>%
  mutate(res_model = class(gam_res)[1])

analysis_res_gam$res_model
```
### GAM Prediction
```{r gam-prediction, cache=FALSE}
analysis_res_e <- analysis_res_gam %>% 
  #=== single average observation ===#
  mutate(profit_data = list(
    get_profit_data(
      data_sf = data,
      est = gam_res
    )
  ))  %>% 
    mutate(vr_rates = list(
    get_vr_rates(
      profit_data = profit_data
    )
  ))  %>% 
    mutate(ur_rate = list(
    get_ur_rate(
      profit_data = profit_data
    )
  ))  %>% 
    mutate(profit_diff = list(
    get_profit_diff(
      profit_data = profit_data,
      ur_rate = ur_rate,
      vr_rates = vr_rates
    )
  ))

analysis_res_e$ur_rate
unique(analysis_res_e$vr_rates[[1]]$treat)

analysis_res_e$profit_diff
```


## Spatial Error Yield Response Function Estimation and Optimal Rates
### Spatial Error Estimation
```{r se, cache=FALSE}
analysis_res_se <- analysis_res_g %>% 
  mutate(se_res = list(
    run_se_ec(data = data)
  )) 
```
### Spatial Error Prediction
```{r se-prediction, cache=FALSE}
analysis_res_se_results <- analysis_res_se %>% 
  #=== single average observation ===#
  mutate(profit_data = list(
    get_profit_data(
      data_sf = data,
      est = se_res
    )
  ))  %>% 
    mutate(vr_rates = list(
    get_vr_rates(
      profit_data = profit_data
    )
  ))  %>% 
    mutate(ur_rate = list(
    get_ur_rate(
      profit_data = profit_data
    )
  ))  %>% 
    mutate(profit_diff = list(
    get_profit_diff(
      profit_data = profit_data,
      ur_rate = ur_rate,
      vr_rates = vr_rates
    )
  ))

analysis_res_se_results$ur_rate
unique(analysis_res_se_results$vr_rates[[1]]$treat)

analysis_res_se_results$profit_diff
```

## SCAM/GAM Analysis Results
### Optimal Maps and EC Relationship
```{r rxmap, cache=FALSE}
data_vr <- data.frame(analysis_res_e$vr_rates[[1]]) %>%
  select(c("obs_id", "treat", "s", "n", "profit_area")) %>%
  dplyr::rename("opt_s" = "s", "opt_n" = "n")
ids <- unique(data_vr$obs_id)

data_sf <- filter(
  data_sf, 
  (obs_id %in% ids))

merge <- merge(data.frame(data_sf), data_vr, by = "obs_id") 

data_sf <- cbind(data_sf, merge)

map_s <- tm_shape(data_sf) +
  tm_polygons(col = "opt_s", lwd = 0.05)

map_n <- tm_shape(data_sf) +
  tm_polygons(col = "opt_n", lwd = 0.05)

opt_map <- tmap_arrange(map_s, map_n)
opt_map
```
### Correlation between EC and Nitrogen 
```{r n-corr}
cor(data_sf$ecs, data_sf$opt_n)
```
### Correlation between EC and Seed 
```{r s-corr}
cor(data_sf$ecs, data_sf$opt_s)
```

## Looking at EC and Soils
### Box Plots of Soil, EC, and Optimal N and S
```{r ec-plots}
plot_data <- st_intersection(data_sf, st_transform_utm(ssurgo))

ggplot(plot_data, aes(x = drainagecl, y = ecs)) +
  geom_boxplot()

ggplot(plot_data, aes(x = soil_name, y = ecs)) +
  geom_boxplot()

ggplot(plot_data, aes(x = erosion, y = ecs)) +
  geom_boxplot()
```
### Boxplots of Optimal Rates and Soil Data
```{r opt-plots}
ggplot(plot_data, aes(x = drainagecl, y = opt_n)) +
  geom_boxplot()

ggplot(plot_data, aes(x = soil_name, y = opt_n)) +
  geom_boxplot()

ggplot(plot_data, aes(x = erosion, y = opt_n)) +
  geom_boxplot()

ggplot(plot_data, aes(x = drainagecl, y = opt_s)) +
  geom_boxplot()

ggplot(plot_data, aes(x = soil_name, y = opt_s)) +
  geom_boxplot()

ggplot(plot_data, aes(x = erosion, y = opt_s)) +
  geom_boxplot()
```

## EC and other Variables
### Correlation between Slope and EC 
```{r corr-slope}
cor.test(data_sf$ecs, data_sf$slope)
```
### Correlation between Elevation and EC 
```{r corr-elevation}
cor.test(data_sf$ecs, data_sf$elevation)
```

### Weather Information
```{r weather}
weather_graph

weather_data
```

### Analysis Result Data
```{r analysis-data}
analysis_results <- data.table(
  "Farm" = w_field_data$farm, 
  "Field" = w_field_data$field,
  "Year" = w_field_data$year,
  "ur_rate" = analysis_res_e$ur_rate[[1]]$treat,
  "min_vr_s" = min(analysis_res_e$vr_rates[[1]]$s),
  "max_vr_s" = max(analysis_res_e$vr_rates[[1]]$s),
  "min_vr_n" = min(analysis_res_e$vr_rates[[1]]$n),
  "max_vr_n" = max(analysis_res_e$vr_rates[[1]]$n),
  "profit_diff" = analysis_res_e$profit_diff[[1]],
  "corr_n" = cor(data_sf$ecs, data_sf$opt_n),
  "corr_s" = cor(data_sf$ecs, data_sf$opt_s))

analysis_results
```

### Spatial Error Analysis Result Data
```{r analysis-data-se}
data_vr_se <- data.frame(analysis_res_se_results$vr_rates[[1]]) %>%
  select(c("obs_id", "treat", "s", "n", "profit_area")) %>%
  dplyr::rename("opt_s" = "s", "opt_n" = "n")
ids <- unique(data_vr_se$obs_id)

data_sf_se <- filter(
  data_sf, 
  (obs_id %in% ids))

merge <- merge(data.frame(data_sf_se), data_vr_se, by = "obs_id") 

data_sf_se <- cbind(data_sf_se, merge)

analysis_results_se <- data.table(
  "Farm" = w_field_data$farm, 
  "Field" = w_field_data$field,
  "Year" = w_field_data$year,
  "ur_rate" = analysis_res_se_results$ur_rate[[1]]$treat,
  "min_vr_s" = min(analysis_res_se_results$vr_rates[[1]]$s),
  "max_vr_s" = max(analysis_res_se_results$vr_rates[[1]]$s),
  "min_vr_n" = min(analysis_res_se_results$vr_rates[[1]]$n),
  "max_vr_n" = max(analysis_res_se_results$vr_rates[[1]]$n),
  "profit_diff" = analysis_res_se_results$profit_diff[[1]],
  "corr_n" = cor(data_sf_se$ecs, data_sf_se$opt_n),
  "corr_s" = cor(data_sf_se$ecs, data_sf_se$opt_s))

analysis_results_se
```

## Saving Results
```{r save, cache=FALSE}
saveRDS(opt_map, here("Data", ffy, "opt_map.rds"))
saveRDS(analysis_res_e, here("Data", ffy, "gam_reg_result.rds"))
saveRDS(analysis_results, here("Data", ffy, "analysis_results.rds"))
saveRDS(analysis_results_se, here("Data", ffy, "analysis_results_se.rds"))
```
